---
title: "Yale Clinical Trials reporting"
author: "Yale Center for Analytical Sciences"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  pdf_document:
    latex_engine: xelatex
classoption: landscape
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{xcolor}
  - \definecolor{ltgray}{HTML}{D3D3D3}
params:
  reg: NA
  res: NA
  data_prospective: NA
  date_min: date_min
  date_max: date_max
  study_type: study_type
  intervention_types: intervention_types
  u_s_fda_regulated_device: u_s_fda_regulated_device
  record_status: record_status
  results_status: results_status
  fdaaa_status: fdaaa_status
  responsible_party: responsible_party
  nih_grants: nih_grants
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F)
library(kableExtra)
library(knitr)
library(tinytex)
#  - \AddToHook{cmd/section/before}{\clearpage}
```

```{r}
reg <- params$reg
res <- params$res
data_prospective <- params$data_prospective
date_min <- params$date_min
date_max <- params$date_max
study_type <- params$study_type
#phase <- params$phase
intervention_types <- params$intervention_types
u_s_fda_regulated_device <- params$u_s_fda_regulated_device
record_status <- params$record_status
results_status <- params$results_status
fdaaa_status <- params$fdaaa_status
#sponsor <- params$sponsor
responsible_party <- params$responsible_party
nih_grants <- params$nih_grants
```

# Data selected

```{r, eval = T}
n <- max(length(study_type), length(intervention_types),
         length(u_s_fda_regulated_device), length(record_status), length(results_status),
         length(fdaaa_status), length(responsible_party), length(nih_grants))

length(study_type) <- n                      
#length(phase) <- n
length(intervention_types) <- n                      
length(u_s_fda_regulated_device) <- n
length(record_status) <- n                      
length(results_status) <- n
length(fdaaa_status) <- n                      
#length(sponsor) <- n
length(responsible_party) <- n                      
length(nih_grants) <- n

selectors = cbind(study_type, intervention_types, u_s_fda_regulated_device, 
                  record_status, results_status, fdaaa_status,
                  responsible_party, nih_grants) %>% 
  as.data.frame()

n<-length(selectors)
m <- n/2
p <- m + 1

selectors[,1:m] %>% 
  #mutate_each(funs(replace(., . %in% c("missing","NA","N/A"), 'Missing'))) %>% 
  distinct() %>% 
  mutate_all(~replace(., is.na(.), '')) %>% 
  rename_all(function(x) gsub("_", " ", x)) %>% 
  rename_all(str_to_title) %>% 
  kbl(., booktabs = T, linesep = "") %>% 
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = F,
                font_size = 8.5)
selectors[,p:n] %>% 
  #mutate_each(funs(replace(., . %in% c("missing","NA","N/A"), 'Missing'))) %>% 
  distinct() %>% 
  mutate_all(~replace(., is.na(.), '')) %>% 
  rename_all(function(x) gsub("_", " ", x)) %>% 
  rename_all(str_to_title) %>% 
  kbl(., booktabs = T, linesep = "") %>% 
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = F,
                font_size = 8.5)
```

\newpage

# Registration report between `r as.yearmon(date_min)` and `r as.yearmon(date_max)`

<!-- , between `r as.yearmon(Sys.Date() %m-% months(12))` and `r as.yearmon(Sys.Date())` -->

```{r, echo = F, eval=T}
#reg$Summary[1] <- rowSums(reg, na.rm = TRUE)
rownames(reg) <-c(
  "Number of records",
  "Average time (days)",
  "Avg CT.gov response time (days) for first try",
  "Average tries",
  "% Success first try",
  "N Success first try",
  "Avg CT.gov response time (days)")

reg %>% 
  mutate_all(~replace(., is.na(.), '')) %>% 
  t() %>% 
  kbl(., booktabs = T, linesep = "") %>% 
  kable_styling(latex_options = c("striped", "hold_position")) %>% 
  column_spec(2:8, width = "6em")
```

\newpage

# Results report, between `r as.yearmon(date_min)` and `r as.yearmon(date_max)`

<!-- , between `r as.yearmon(Sys.Date() %m-% months(12))` and `r as.yearmon(Sys.Date())` -->

```{r, echo = F, eval=T}
rownames(res) <- c(
  "Number of records submitted",
  "Number of records published", # if initial_results = NA
  "Average days to publish",
  "Avg CT.gov response time \n (days) for first try",
  "Average tries",
  "% Success first try",
  "N Success first try",
  "Avg CT.gov response time (days)",
  "Reported within 12mo",
  "Avg days since \n primary completion date"
)

res %>% 
  mutate_all(~replace(., is.na(.), '')) %>% 
  t() %>% 
  kbl(., booktabs = T, linesep = "") %>% 
  kable_styling(latex_options = c("striped", "hold_position")) %>% 
  column_spec(2:11, width = "5em")
```

\newpage

# Prospective

## Expected updates and results in next quarter,

### between `r as.yearmon(Sys.Date())` and `r as.yearmon(Sys.Date() %m+% months(3))`

```{r, eval = T}
data_prospective %>%
  group_by(`Record Type`, `Update Type`) %>% 
  summarise(`Number of Records` = n()) %>% 
  kbl(., booktabs = T, linesep = "")

```

```{r, eval = T}
# cell styling
# not act, pact, but is NIH, then check - NIH but not FDAAA >> check mark
data_prospective$NIH <- ifelse(data_prospective$NIH == "NIH", 
                                 cell_spec(data_prospective$NIH, color = "blue"), 
                                 "")
data_prospective$`Update Type` <- ifelse(str_detect(data_prospective$`Update Type`,"Results"), 
                                         cell_spec(data_prospective$`Update Type`, color = "red"), 
                                         data_prospective$`Update Type`)

# escape "_" b/c latex doesn't like it
data_prospective$`Protocol Id`  <- gsub("_", " ", data_prospective$`Protocol Id`) # space
```


Note: $\textcolor{blue}{\textbf{NIH}}$ signifies an NIH-defined clinical trial


$\textcolor{red}{\textbf{All results}}$ or $\textcolor{red}{\textbf{Results}}$ expected are colored red, ${\textbf{Updates}}$ expected are not colored

\newpage

### Registration

```{r, eval=T}
data_prospective_r <- data_prospective %>% 
  filter(`Record Type` == "Registration") %>% 
  select(-c(`Record Type`, `Brief Title`, `Overall Status`:Problems)) 
# special characters in title will cause compile issues

kbl(data_prospective_r, booktabs = T, format = "latex",  
    escape = F, longtable = T, linesep = "") %>% 
  kable_styling(latex_options = c("striped", "repeat_header"),
                full_width = F,
                font_size = 8.5)
```

\newpage

### Results

```{r, eval=T}
data_prospective %>% 
  filter(`Record Type` == "Results") %>% 
  select(-c(`Record Type`,`Brief Title`, `Overall Status`:Problems)) %>% 
  knitr::kable(., format="latex", booktabs = T, escape = F, longtable = T, linesep = "") %>% 
  kable_styling(latex_options = c("striped", "repeat_header"),
                full_width = F,
                font_size = 8.5) 
```
